\documentclass{article} % For LaTeX2e
\usepackage{iclr2022_conference,times}
% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

%######## APS360: Uncomment your submission name
%\newcommand{\apsname}{Project Proposal}
%\newcommand{\apsname}{Progress Report}
\newcommand{\apsname}{Final Report}

%######## APS360: Put your Group Number here
\newcommand{\gpnumber}{40}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
%######## APS360: Put your project Title here
\title{Image Colourization via Convolutional \\
Neural Networks and Deep Learning}


%######## APS360: Put your names, student IDs and Emails here
\author{Harkirpa Kaur  \\
Student\# 1011242479 \\
\texttt{harkirpa.kaur@mail.utoronto.ca}} \\


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy 
%######## APS360: Document starts here
\begin{document}


\maketitle
%######## APS360: Do not change the next line. This shows your Main body page count.
----Total Pages: \pageref{last_page}

\section{Contributions}

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Harkirpa & Peter & Thulasi & Youssef \\
24\% & 23\% & 26\% & 27\% \\
\hline
\end{tabular}
\caption{Contribution percentages by team member}
\label{tab:contributions}
\end{table}

I was responsible for several tasks as the team worked through the image colorization project. Starting with the progress report, I researched factors that facilitated the need for image colorization and
the history of colourized photography. I researched and compiled possible ethical considerations related to image colorization. For the progress report, I wrote the individual contributions section
and updated the Gantt chart. I also researched and implemented techniques to decrease run time for our primary model. Our model was also facing an issue with avoiding vibrant colours and resorting
to brown hues. To combat this, I researched and implemented a quantized bin classification method in our existing model. However, this method was not implemented in the final model. For the final
report, I wrote the quantitative results section and updated the slideshow accordingly. I also wrote code to run our primary model on the test dataset and show sample outputs.
Throughout the project, the team held weekly meetings to discuss progress and next steps for the project. The meetings were led on a rotating basis such that each team member prepared the meeting
agenda for and led 25\% of all meetings.

Of the tasks I undertook, there were some that I was unable to complete. These included writing the abstract for the project proposal and working on the initial version of the primary
model. The abstract was written by another team member, as they had finished their assigned parts early. The initial primary model was assigned to Youssef and me; however, we faced difficulties
collaborating on Google Colab in addition to being in different time zones. To optimize time management, the team agreed to have Youssef write the code for the initial primary model, and we agreed
to collaborate on any other versions of the model we may have to create, such as the quantized bin version.

Overall, all team members put in a roughly equal amount of work, and we are all satisfied with thequality and quantity of each member’s work.
\label{last_page}

\end{document}
