\documentclass{article} % For LaTeX2e
\usepackage{iclr2022_conference,times}
% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

%######## APS360: Uncomment your submission name
%\newcommand{\apsname}{Project Proposal}
%\newcommand{\apsname}{Progress Report}
\newcommand{\apsname}{Final Report}

%######## APS360: Put your Group Number here
\newcommand{\gpnumber}{40}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}

%######## APS360: Put your project Title here
\title{Image Colourization via Convolutional \\
Neural Networks and Deep Learning}


%######## APS360: Put your names, student IDs and Emails here
\author{Youssef Fikry  \\
Student\# 1006682626\\
\texttt{youssef.fikry@mail.utoronto.ca} \\
\And Harkirpa Kaur  \\
Student\# 1011242479 \\
\texttt{harkirpa.kaur@mail.utoronto.ca} \\
\AND
Peter Leong \\
Student\# 1010892955 \\
\texttt{peter.leong@mail.utoronto.ca} \\
\And
Thulasi Thavarajah \\
Student\# 10115358424 \\
\texttt{t.thavarajah@mail.utoronto.ca} \\
\AND
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy 
%######## APS360: Document starts here
\begin{document}


\maketitle

\begin{abstract}
This project addresses the challenge of automated colourization for 256$\times$256 grayscale images using a dataset of 12,600 image pairs, balanced across human subjects, 
animals, and natural scenery. We frame colourization as a supervised learning problem in the CIELAB colour space, where a model predicts chrominance channels ($a^*$, $b^*$) 
from the luminance channel ($L^*$). A shallow convolutional neural network (CNN) provides the baseline performance, while our primary solution employs a deeper convolutional 
encoder-decoder architecture. This design captures high-level semantic features and spatial context, addressing limitations of shallow networks in perceptual realism. All 
source code, datasets, and results are publicly available \href{https://drive.google.com/drive/folders/1cV1NhlQ8UTk_CgJdwhqeRu0z5xE85ZsI?usp=sharing}{here}. 
%######## APS360: Do not change the next line. This shows your Main body page count.
----Total Pages: \pageref{last_page}
\end{abstract}



\section{Introduction}

While colour photography processes first emerged in the 1890s, colour photography did not become widely accessible until the 1970s \citep{scienceandmediamuseum2020}. 
Consequently, most historical photographs remain in black and white, lacking the visual richness that modern viewers are accustomed to. Moreover, individuals who undergo cataract 
removal as part of vision restoration procedures often struggle to interpret grayscale images, rendering many historical photographs inaccessible to them \citet{vogelsang2024impact}. 
This project aims to leverage deep learning to automatically colourize black and white images, with the goal of restoring visual information and improving accessibility for all audiences. 
Traditional, non-deep learning colourization methods tend to produce desaturated results and require extensive human input, limiting their scalability \citep{cheng2016deepcolorization}. 
In contrast, deep neural networks such as convolutional neural networks (CNNs) can effectively learn spatial and semantic features, enabling realistic colourization without user 
intervention \citep{zhang2016colorful}. This makes deep learning a promising and scalable solution for image colourization.

\section{Contributions}

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Harkirpa & Peter & Thulasi & Youssef \\
24\% & 23\% & 26\% & 27\% \\
\hline
\end{tabular}
\caption{Contribution percentages by team member}
\label{tab:contributions}
\end{table}

I was responsible for several tasks as the team worked through the image colorization project. Starting with the progress report, 
I researched factors that facilitated the need for image colorization and the history of colorized photography. I also did research
for the ethical considerations portion of the report. Next, for the progress report I wrote the individual contributions section and updated the gantt
chart. At this time, our model was facing an issue with avoiding vibrant colours and resorting to brown hues. Each of the members were responsible
for implementing one possible solution, and I worked on changing our primary model to use quantized bins, however this method was not implemented
in the final model. For the final report, I wrote the quantitative results section and updated the slideshow accordingly. Throughout the duration of the project,
the team had weekly meetings which were lead on a rotating basis, such that each team member was responsible for preparing the meeting agenda and leading 25\% of all meetings.

In addition, there were some tasks which I was assigned but unable to complete. These include writing the abstract for the project proposal and working on the initial version of the primary model.
The abstract was completed by another team member as they had finished their assigned parts early. The initial primary model was assigned to Youssef and I, however we found 
it difficult to collaborate using Google Colab in addition to a large difference in time zones, so we agreed to have Youssef code the initial model. 

\label{last_page}
\newpage
\bibliography{APS360_ref}
\bibliographystyle{iclr2022_conference}

\end{document}
